---
title: "TT20230711"
author: "Noah Lee"
date: "2023-07-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(tidyverse)
```

## Instructions
```{r}
# Get the Data

# Read in with tidytuesdayR package 
# Install from CRAN via: install.packages("tidytuesdayR")

global_temps <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-07-11/global_temps.csv')
nh_temps <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-07-11/nh_temps.csv')
sh_temps <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-07-11/sh_temps.csv')
zonann_temps <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-07-11/zonann_temps.csv')

```


## The Data
```{r}
head(global_temps)
head(nh_temps)
head(sh_temps)
head(zonann_temps)
```


## Plot graphs connected with line

August of Global
```{r}
ggplot(data = global_temps, aes(x = Year, y=Aug)) +
  geom_point() + geom_line() + ylab("AVG change of temp in August")
```


August of Northern hemisphere
```{r}
ggplot(data = nh_temps, aes(x = Year, y=Aug)) +
  geom_point() + geom_line() + ylab("AVG change of temp in August")
```


August of Southern hemisphere
```{r}
ggplot(data = sh_temps, aes(x = Year, y=Aug)) +
  geom_point() + geom_line() + ylab("AVG change of temp in August")
```



Combine Northen and Southern hemisphere data for August
```{r}
ggplot() +
  geom_line(data=nh_temps, aes(x=Year, y=Aug), colour = "red") +
  geom_smooth(data=nh_temps, aes(x=Year, y=Aug), colour = "red") +
  geom_line(data=sh_temps, aes(x=Year, y=Aug), colour = "blue") +
  geom_smooth(data=sh_temps, aes(x=Year, y=Aug), colour = "blue")
```



# Creating overall graph
Create 1 graph using all meteorological seasons, and another using the D-N variable. In the end, the graphs should be
almost identical.

- Creating a graph using the meteorological season variables DJF, MAM, JJA, and SON.
```{r}
metsea4 <- c()

for (row in 1:nrow(global_temps)) {
  temp1 <- global_temps[[row, 16]]
  temp2 <- global_temps[[row, 17]]
  temp3 <- global_temps[[row, 18]]
  temp4 <- global_temps[[row, 19]]
  metsea4 <- append(metsea4, temp1)
  metsea4 <- append(metsea4, temp2)
  metsea4 <- append(metsea4, temp3)
  metsea4 <- append(metsea4, temp4)
}

#length(metsea4)
metsea.global <- data.frame(season = 1:576)
metsea.global$dev <- metsea4
#metsea.global    #data per meteorological season
```

```{r}
metsea4gg <- metsea.global[2:574,]

ggplot(data = metsea4gg, aes(x=season, y=dev)) + 
  geom_point() + geom_line() + ylab("Deviation from AVG per season")
```


- Creating a graph using the meteorological year variable D-N.
```{r}
DNdata <- c()

for (row in 1:nrow(global_temps)) {
  temp <- global_temps[[row, 15]]
  DNdata <- append(DNdata, temp)
}

DNcomp <- data.frame(year = 1:144)
DNcomp$dev <- DNdata
#DNcomp    #data per meteorological year
```

```{r}
DNgg <- DNcomp[2:143,]

ggplot(data = DNgg, aes(x=year, y=dev)) + 
  geom_point() + geom_line() + ylab("Deviation from AVG per year")
```
